A standard for the scholarly citation of archaeological data as an incentive to data sharing

### 2017-12-29 analysis/paper/paper.Rmd
working on reference list

Dorch, B. F., Drachen, T. M., and O. Ellegaard
2015	The Data Sharing Advantage in Astrophysics. Proceedings of the International Astronomical Union, 11(A29A), 172-175.

Duke, C. S., and J. H. Porter
2013.	The Ethics of Data Sharing and Reuse in Biology. BioScience, 63(6), 483–489. 
Editors
2013.	Guide for Authors. Journal of Archaeological Science. Electronic document, https://web.archive.org/web/20130125222940/https://www.elsevier.com/journals/journal-of-archaeological-science/0305-4403/guide-for-authors, accessed 7 September 7, 2017
Ellison, L. A. 
2012.	Just 20 days left!! Upload Your Archaeological Information FREE to tDAR!! | The Digital Archaeological Record (blog). Electronic document https://www.tdar.org/news/2012/12/just-20-days-left-upload-your-archaeological-information-free-to-tdar/, accessed 7 September 2017
Eglen, S. J., Marwick, B., Halchenko, Y. O., Hanke, M., Sufi, S., Gleeson, P., J.-B. Poline
2017.	Toward Standard Practices for Sharing Computer Code and Programs in Neuroscience. Nature Neuroscience, 20(6), 770–773. 
Fienberg, S. E., Martin, M. E., & Straf, M. L. 
1985	Sharing Research Data. National Academy Press, Washington DC.
Floridi, L. 
2011.	The Philosophy of Information. Oxford University Press, London.
Giofrè, D., Cumming, G., Fresc, L., Boedker, I., and P. Tressoldi
2017.	The influence of journal submission guidelines on authors’ reporting of statistics and use of open research practices. PLoS ONE, 12(4). DOI:10.1371/journal.pone.0175583, accessed on 7 September 2017
Gleditsch, N. P., Metelits, C., and H. Strand
2003.	Posting Your Data: Will You be Scooped or will You be Famous. International Studies Perspectives, 4(1), 89-97.
Hacking I.
1992.	The Self-Vindication of the Laboratory Sciences. In Science as Practice and Culture, edited by Andrew Pickering. The University of Chicago Press, pp. 29–64, Chicago, Illinois. 
Hagstrom, W O. 
1982.	Gift Giving as an Organising Principle in Science In Science in Context: Readings in the Sociology of Science edited by B. Barnes and D. Edge, pp. 21–34, The Open University Press, Milton Keynes. 
Harding, A., Harper, B., Stone, D., O’Neill, C., Berger, P., Harris, S., and J. Donatuto
2012.	Conducting Research with Tribal Communities: Sovereignty, Ethics, and Data-Sharing Issues. Environmental Health Perspectives, 120(1), 6.
Hart, E. M., Barmby, P., LeBauer, D., Michonneau, F., Mount, S., Mulrooney, P., and , J. W. Hollister
2016.	Ten Simple Rules for Digital Data Storage. PLOS Computational Biology, 12(10), e1005097. DOI:10.1371/journal.pcbi.1005097, accessed on 7 September 2017
Henneken, E. A., and A. Accomazzi
2011.	Linking to Data-Effect on Citation Rates in Astronomy. Electronic document, https://arxiv.org/abs/1111.3618, accessed 17 September 2017
Huggett, J. 
2017	Citing Data Reuse. Electronic document, https://introspectivedigitalarchaeology.wordpress.com/2017/05/23/citing-data-reuse/, accessed September 7, 2017
Hymes, D. 
1972.	Reinventing Anthropology. Pantheon, New York.
Inter-university Consortium for Political and Social Research
2012.	Guide to Social Science Data Preparation and Archiving: Best Practice Throughout the Data Life Cycle (5th ed.). Institute for Social Research University of Michigan, Ann Arbor, Michigan
Kansa, E. C. and S. W. Kansa
2013.	Open Archaeology: We All Know That a 14 Is a Sheep: Data Publication and Professionalism in Archaeological Communication. Journal of Eastern Mediterranean Archaeology & Heritage Studies, 1(1), 88-97.
Kansa, E. C., S. W. Kansa and E. Watrall, E. (editors)
2011.	Archaeology 2.0: new approaches to communication and collaboration. Cotsen Digital Archaeology Series, University of California, Electronic document, https://escholarship.org/uc/item/1r6137tb, accessed 7 November 2017
Kidwell, M. C., Lazarević, L. B., Baranski, E., Hardwicke, T. E., Piechowski, S., Falkenberg, L. S. and T. M. Errington
2016.	Badges to Acknowledge Open Practices: A Simple, Low-cost, Effective Method for Increasing Transparency. PLoS Biology, 14(5), e1002456.
Kintigh, K. 
2006.	The Promise and Challenge of Archaeological Data Integration. American Antiquity, 71(3), 567-578.
Keers, G., van der Reijden, H., and H. van Rossum
2011.	Planning Archaeology: A Synthesis of the Thematic Sub-reports. RIGO Research en Advies, Amsterdam. 
Kratz J. and C. Strasser 
2015.	 Researcher Perspectives on Publication and Peer Review of Data. PLOS ONE 10(2): e0117619. DOI:10.1371/journal.pone.0117619, accessed 7 September 2017.
Kratz J. and C. Strasser 
2014.	Data publication consensus and controversies [version 1; referees: 1 approved with reservations]. F1000Research, Electronic document, https://f1000research.com/articles/3-94/v1, accessed 7 September 2017.
Kyzas P.A, K.T. Loizou, and J.P. Ioannidis
2005.	Selective reporting biases in cancer prognostic factor studies. Journal of the National Cancer Institute 97, 1043-1055.
Latour, B. 
1999.	Pandora's Hope: Essays on the Reality of Science Studies. Harvard University Press, Massachusetts. 

>>>>

Dorch, Bertil. F., Thea M. Drachen, and Ole Ellegaard
2015	The Data Sharing Advantage in Astrophysics. _Proceedings of the International Astronomical Union_ 11(A29A): 172-175.

Duke, Clifford S. and John H. Porter
2013	The Ethics of Data Sharing and Reuse in Biology. BioScience, 63(6): 483–489.

Editors
2013.	Guide for Authors. Journal of Archaeological Science. Electronic document, https://web.archive.org/web/20130125222940/https://www.elsevier.com/journals/journal-of-archaeological-science/0305-4403/guide-for-authors, accessed 7 September 7, 2017

Ellison, Leigh A. 
2012.	Just 20 days left!! Upload Your Archaeological Information FREE to tDAR!! _The Digital Archaeological Record_ (blog). Electronic document https://www.tdar.org/news/2012/12/just-20-days-left-upload-your-archaeological-information-free-to-tdar/, accessed 7 September 2017

Eglen, Stephen. J., Ben Marwick, Yaroslav O. Halchenko, Michael Hanke, Shoaib Sufi, Padraig Gleeson, Jean-Baptist Poline
2017	Toward Standard Practices for Sharing Computer Code and Programs in Neuroscience. _Nature Neuroscience_ 20(6), 770–773.

Fienberg, Stephen E., Margaret E. Martin, & Miron L. Straf 
1985	_Sharing Research Data_. National Academy Press, Washington DC.

Floridi, Luciano
2011	The Philosophy of Information. Oxford University Press, London.

Giofrè, David, Geoff Cumming, Luca Fresc, Ingrid Boedker and Patrizio Tressoldi
2017	The influence of journal submission guidelines on authors’ reporting of statistics and use of open research practices. _PLoS ONE_ 12(4). DOI:10.1371/journal.pone.0175583, accessed on 7 September 2017

Gleditsch, Nils. P., Claire Metelits and Håvard Strand
2003	Posting Your Data: Will You be Scooped or will You be Famous. _International Studies Perspectives_ 4(1): 89-97.

Hacking, Ian
1992	The Self-Vindication of the Laboratory Sciences. In _Science as Practice and Culture_, edited by Andrew Pickering. The University of Chicago Press, pp. 29–64, Chicago, Illinois.

Hagstrom, Warren O. 
1982	Gift Giving as an Organising Principle in Science. In _Science in Context: Readings in the Sociology of Science_ edited by B. Barnes and D. Edge, pp. 21–34, The Open University Press, Milton Keynes.

Harding, Anna, Barbara Harper, Dave Stone, Catherine O’Neill, Patricia Berger, Stuart Harris and Jamie Donatuto
2012	Conducting Research with Tribal Communities: Sovereignty, Ethics, and Data-Sharing Issues. _Environmental Health Perspectives_ 120(1): 6-10.

Hart, Edmund M., Pauline Barmby, David LeBauer, François Michonneau, Sarah Mount, Patrick Mulrooney and Jeffrey. W. Hollister
2016	Ten Simple Rules for Digital Data Storage. _PLOS Computational Biology_ 12(10), e1005097. DOI:10.1371/journal.pcbi.1005097, accessed on 7 September 2017

Henneken, Edwin A., and Alberto Accomazzi
2011	Linking to Data-Effect on Citation Rates in Astronomy. Electronic document, https://arxiv.org/abs/1111.3618, accessed 17 September 2017

Huggett, Jeremy 
2017	Citing Data Reuse. Electronic document, https://introspectivedigitalarchaeology.wordpress.com/2017/05/23/citing-data-reuse/, accessed September 7, 2017

Hymes, Dell 
1972	_Reinventing Anthropology_. Pantheon, New York.

Inter-university Consortium for Political and Social Research
2012	_Guide to Social Science Data Preparation and Archiving: Best Practice Throughout the Data Life Cycle_ (5th ed.). Institute for Social Research University of Michigan, Ann Arbor, Michigan

Kansa, Eric C. and Sarah W. Kansa
2013	Open Archaeology: We All Know That a 14 Is a Sheep: Data Publication and Professionalism in Archaeological Communication. _Journal of Eastern Mediterranean Archaeology & Heritage Studies_ 1(1): 88-97.

Kansa, Eric C., Sarah. W. Kansa and Ethan Watrall (editors)
2011	_Archaeology 2.0: new approaches to communication and collaboration_. Cotsen Digital Archaeology Series, University of California, Electronic document, https://escholarship.org/uc/item/1r6137tb, accessed 7 November 2017

Kidwell, Mallory C., Ljiljana B. Lazarević, Erica Baranski, Tom Hardwicke, Sarah Piechowski, Lina-Sophia Falkenberg and Brian Nosek
2016	Badges to Acknowledge Open Practices: A Simple, Low-cost, Effective Method for Increasing Transparency. _PLoS Biology_ 14(5), e1002456.

Kintigh, Keith 
2006.	The Promise and Challenge of Archaeological Data Integration. _American Antiquity_ 71(3): 567-578.

Keers, Geurt, Hans van der Reijden and Hans van Rossum
2011	_Planning Archaeology: A Synthesis of the Thematic Sub-reports_. RIGO Research en Advies, Amsterdam.

Kratz John and Carly Strasser 
2015	 Researcher Perspectives on Publication and Peer Review of Data. _PLOS ONE_ 10(2): e0117619. DOI:10.1371/journal.pone.0117619, accessed 7 September 2017.

Kratz John and Carly Strasser 
2014	Data publication consensus and controversies [version 1; referees: 1 approved with reservations]. F1000Research, Electronic document, https://f1000research.com/articles/3-94/v1, accessed 7 September 2017.

Kyzas Panayiotis A., Konstantinos T. Loizou and John P. A. Ioannidis
2005.	Selective reporting biases in cancer prognostic factor studies. _Journal of the National Cancer Institute_ 97: 1043-1055.

Latour, Bruno 
1999	_Pandora's Hope: Essays on the Reality of Science Studies_. Harvard University Press, Massachusetts.
